Followers Are Not Enough: Beyond Structural Communities in Online Social Networks

### 2014-07-14 paper-for_arxiv/paper.tex
Minor changes to acknowledgments section.

Thanks to Cesar Flores, Lu\'is Seoane, Kevin Stadler, Jody Wright, and Nix Barnett to their contributions of preliminary ideas related to this paper and to Michelle Girvan, William Rand, and Aaron Clauset for their valuable comments and suggestions. This work was partially

>>>>

Thanks to Cesar Flores, Lu\'is Seoane, Kevin Stadler, Jody Wright, and Nix Barnett for their contributions to preliminary ideas related to this paper and to Michelle Girvan, William Rand, and Aaron Clauset for their valuable comments and suggestions. This work was partially funded by...
